The 300 km~s$^{-1}$ stellar stream near Segue\,1: Insights From High-Resolution Spectroscopy of its brightest star

### 2012-11-15 2012-segue-1/segue_draft2.tex
Draft 2 of segue paper

\subsection{Stream Membership}
As demonstrated by other authors, there is unequivocally a coherent stream present here with a kinematic peak $v_{helio} = 300$ km s$^{-1}$ \citep{Geha2009, Norris2010, Simon2011}. At more extreme velocities, halo contaminants become less likely. Given that a stream is present here with high velocities, it is worth quantifying the likelihood whether the star analysed here is a contaminant or not. As a comparison we have queried a the Besan\c{c}on model \citep{Robin2003} with a $1^\circ$ cone for representative halo metallicities and kinematics in this region. A two-sample Kolmogorov–Smirnov test with kinematics yields a $p = 0.097$, or an $\sim10$\% chance that the star analysed here is a halo contaminant. When coupled with metallicity, it is clear that this star sits separate from the main halo population (Figure \ref{fig:besancon}). We note that the same probability cutoff was employed by \citet{Simon2011} in order to examine stream members.

>>>>

\subsection{Stream Membership}
As demonstrated by other authors, there is unequivocally a coherent stream present here with a kinematic peak $v_{helio} = 300$ km s$^{-1}$ \citep{Geha2009, Norris2010, Simon2011}. At more extreme velocities, halo contaminants become less likely. Given that a stream is present here with high velocities, it is worth quantifying the likelihood whether the star analysed here is a contaminant or not.
We have employed a two-sample Kolmogorov-Smirnov test using the predicted line-of-sight velocities in the Besan\c{c}on model \citep{Robin2003} to quantify the liklihood whether this star, 300S-1, likely belongs to the halo or not. We yield a $p$ value of $0.097$, or a $\sim10$\% chance that 300S-1 is a halo contaminant.

When coupled with metallicity, it is clear that this star sits separate from the main line-of-sight population (Figure \ref{fig:besancon}). We note that the same probability cutoff found here ($\lesssim10$\%) was employed by \citet{Simon2011} in order to examine stream members.
